### 2014-07-29 paper/paper.tex
Wrote more things

            \item Then \textbf{Uncommon words} are removed. Words that do not
                meet a certain document frequency threshold are eliminated.
                Many of these words are proper nouns that, if retained are
                likely to cause the classifier to overfit to the training set

@@

    \item \textbf{Training}
    \item \textbf{Testing}
\end{enumerate}

>>>>

            \item Then \textbf{Uncommon words} are removed. Words that do not
                meet a certain document frequency threshold are eliminated.
                Many of these words are proper nouns that, if retained are
                likely to cause the classifier to overfit to the training set.

@@

    \item \textbf{Splitting} - The corpus of documents are random separated
        into three sets: the \textit{training set}, the \textit{validation set},
        and the \textit{testing set}. Respectively, Each dataset is 60\%, 20\%,
        and 20\% of the corpus.

    \item \textbf{Training} -

    \item \textbf{Testing} - The performance of the dataset is evaulated
        against the \textit{testing set}.

\end{enumerate}
